Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?

### 2022-09-20 SIOP2023/Counts/Submission_ResourceCount.Rmd
inefficient recoeds

---
title: "Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?"
output:
  pdf_document: 
    latex_engine: xelatex
---

@@

knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)
#knitr::opts_knit$set(root.dir=normalizePath('../'))
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

@@

data22 <- data %>% 
mutate_at(vars(118:372),
function(x) recode(x,
1==NA, 
2==NA,
3==NA,
4==4,
5==5))

@@

data22$resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
data22$hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
data22$challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)

data22$item387 <- 7-data22$item387
data22$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
data22$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
data22$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some

cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges

@@

data22$rh1  <- data22$item118 + data22$item203
data22$rh2  <- data22$item119 + data22$item204
data22$rh3  <- data22$item120 + data22$item205
data22$rh4  <- data22$item121 + data22$item206
data22$rh5  <- data22$item122 + data22$item207
data22$rh6  <- data22$item123 + data22$item208
data22$rh7  <- data22$item124 + data22$item209
data22$rh8  <- data22$item125 + data22$item210
data22$rh9  <- data22$item126 + data22$item211
data22$rh10 <- data22$item127 + data22$item212
data22$rh11  <- data22$item128 + data22$item213
data22$rh12  <- data22$item129 + data22$item214
data22$rh13  <- data22$item130 + data22$item215
data22$rh14  <- data22$item131 + data22$item216
data22$rh15  <- data22$item132 + data22$item217
data22$rh16  <- data22$item133 + data22$item218
data22$rh17  <- data22$item134 + data22$item219
data22$rh18  <- data22$item135 + data22$item220
data22$rh19  <- data22$item136 + data22$item221
data22$rh20  <- data22$item137 + data22$item222
data22$rh21  <- data22$item138 + data22$item223
data22$rh22  <- data22$item139 + data22$item224
data22$rh23  <- data22$item140 + data22$item225
data22$rh24  <- data22$item141 + data22$item226
data22$rh25  <- data22$item142 + data22$item227
data22$rh26  <- data22$item143 + data22$item228
data22$rh27  <- data22$item144 + data22$item229

data22$rh28  <- data22$item146 + data22$item230

data22$rh29  <- data22$item147 + data22$item231
data22$rh30  <- data22$item148 + data22$item232
data22$rh31  <- data22$item149 + data22$item233
data22$rh32  <- data22$item150 + data22$item234
data22$rh33  <- data22$item151 + data22$item235
data22$rh34  <- data22$item152 + data22$item236
data22$rh35  <- data22$item153 + data22$item237
data22$rh36  <- data22$item154 + data22$item238
data22$rh37  <- data22$item155 + data22$item239
data22$rh38  <- data22$item156 + data22$item240
data22$rh39  <- data22$item157 + data22$item241
data22$rh40  <- data22$item158 + data22$item242
data22$rh41  <- data22$item159 + data22$item243
data22$rh42  <- data22$item160 + data22$item244
data22$rh43  <- data22$item161 + data22$item245
data22$rh44  <- data22$item162 + data22$item246
data22$rh45  <- data22$item163 + data22$item247

data22$rh46  <- data22$item164 + data22$item249

data22$rh47  <- data22$item165 + data22$item250
data22$rh48  <- data22$item166 + data22$item251
data22$rh49  <- data22$item167 + data22$item252
data22$rh50  <- data22$item168 + data22$item253
data22$rh51  <- data22$item169 + data22$item254
data22$rh52  <- data22$item170 + data22$item255
data22$rh53  <- data22$item171 + data22$item256
data22$rh54  <- data22$item172 + data22$item257
data22$rh55  <- data22$item173 + data22$item258
data22$rh56  <- data22$item174 + data22$item259
data22$rh57  <- data22$item175 + data22$item260
data22$rh58  <- data22$item176 + data22$item261
data22$rh59  <- data22$item177 + data22$item262
data22$rh60  <- data22$item178 + data22$item263
data22$rh61  <- data22$item179 + data22$item264
data22$rh62  <- data22$item180 + data22$item265
data22$rh63  <- data22$item181 + data22$item266
data22$rh64  <- data22$item182 + data22$item267
data22$rh65  <- data22$item183 + data22$item268
data22$rh66  <- data22$item184 + data22$item269
data22$rh67  <- data22$item185 + data22$item270
data22$rh68  <- data22$item186 + data22$item271
data22$rh69  <- data22$item187 + data22$item272
data22$rh70  <- data22$item188 + data22$item273
data22$rh71  <- data22$item189 + data22$item274
data22$rh72  <- data22$item190 + data22$item275
data22$rh73  <- data22$item191 + data22$item276
data22$rh74  <- data22$item192 + data22$item277
data22$rh75  <- data22$item193 + data22$item278
data22$rh76  <- data22$item194 + data22$item279
data22$rh77  <- data22$item195 + data22$item280
data22$rh78  <- data22$item196 + data22$item281
data22$rh79  <- data22$item197 + data22$item282
data22$rh80  <- data22$item198 + data22$item283
data22$rh81  <- data22$item199 + data22$item284
data22$rh82  <- data22$item200 + data22$item285
data22$rh83  <- data22$item201 + data22$item286
data22$rh84  <- data22$item202 + data22$item287

@@

data22$rc1  <- data22$item118 + data22$item288
data22$rc2  <- data22$item119 + data22$item289
data22$rc3  <- data22$item120 + data22$item290
data22$rc4  <- data22$item121 + data22$item291
data22$rc5  <- data22$item122 + data22$item292
data22$rc6  <- data22$item123 + data22$item293
data22$rc7  <- data22$item124 + data22$item294
data22$rc8  <- data22$item125 + data22$item295
data22$rc9  <- data22$item126 + data22$item296
data22$rc10 <- data22$item127 + data22$item297
data22$rc11  <- data22$item128 + data22$item298
data22$rc12  <- data22$item129 + data22$item299
data22$rc13  <- data22$item130 + data22$item300
data22$rc14  <- data22$item131 + data22$item301
data22$rc15  <- data22$item132 + data22$item302
data22$rc16  <- data22$item133 + data22$item303
data22$rc17  <- data22$item134 + data22$item304
data22$rc18  <- data22$item135 + data22$item305
data22$rc19  <- data22$item136 + data22$item306
data22$rc20  <- data22$item137 + data22$item307

data22$rc21  <- data22$item138 + data22$item309

data22$rc22  <- data22$item139 + data22$item310
data22$rc23  <- data22$item140 + data22$item311
data22$rc24  <- data22$item141 + data22$item312
data22$rc25  <- data22$item142 + data22$item313
data22$rc26  <- data22$item143 + data22$item314
data22$rc27  <- data22$item144 + data22$item315

data22$rc28  <- data22$item146 + data22$item316

>>>>

---
title             : "Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?"
shorttitle        : "BiFactor Engagement"

author: 
  - name          : "John Kulas"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1 Normal Ave, Montclair, NJ 07043"
    email         : "kulasj@montclair.edu"
  - name          : "Renata Garcia Prieto Palacios Roji"
    affiliation   : "1"
  - name          : "Casey Osorio-Duffoo"
    affiliation   : "2"
  - name          : "Morgan Russell"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Montclair State University"
  - id            : "2"
    institution   : "Harver"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  The most commonly referenced definition of attitudinal engagement implicates sub-dimensions of vigor, dedication, and absorption. The tripartite model of attitudes specifies cognitive, behavioral, and affective components. The current study documents the development and initial validation of a new measure of engagement that intentionally crosses the substantive and attitudinal elements.

keywords          : "Engagement, engagement"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no #change to yes if we want all tables to be put in-line rather than pushed to end of paper
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)
#knitr::opts_knit$set(root.dir=normalizePath('../'))
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
papaja::r_refs("r-references.bib")

@@

# data22 <- data %>% 
# mutate_at(vars(118:372),
# function(x) recode(x,
# 1==NA, 
# 2==NA,
# 3==NA,
# 4==4,
# 5==5))

@@

data$resource <- rowSums(data[c(118:144,146:202)], na.rm=TRUE)
data$hindrance <- rowSums(data[c(203:247,249:287)], na.rm=TRUE)
data$challenge <- rowSums(data[c(288:307,309:372)], na.rm=TRUE)

data$item387 <- 7-data$item387
data$burnout      <- rowMeans(data[c(373:376)], na.rm=TRUE)
data$stress       <- rowMeans(data[c(377:379)], na.rm=TRUE)
data$engagement   <- rowMeans(data[c(380:399)], na.rm=TRUE)        ## probably need to recode some

cor(data[405:410], use="all.obs")   ## something to be told with resources and challenges

@@

data$rh1[data$item118 > 3 & data$item203 > 3 & data$item22 >  1] <- 1        ## characteristic also both
data$rh1[data$item22 == 1] <- NA                                             ## Not a characteristic
data$rh1[(data$item118 < 4 | data$item203 < 4) & data$item22 >  1] <- 0      ## characteristic but not both

data$rh2[ data$item119 > 3 & data$item204 > 3 &  data$item23 >  1] <- 1        
data$rh2[(data$item119 < 4 | data$item204 < 4) & data$item23 >  1] <- 0
data$rh2[                                        data$item23 == 1] <- NA

data$rh3[ data$item120 > 3 & data$item205 > 3 &  data$item24 >  1] <- 1        
data$rh3[(data$item120 < 4 | data$item205 < 4) & data$item24 >  1] <- 0
data$rh3[                                        data$item24 == 1] <- NA

data$rh4[ data$item121 > 3 & data$item206 > 3 &  data$item25 >  1] <- 1        
data$rh4[(data$item121 < 4 | data$item206 < 4) & data$item25 >  1] <- 0
data$rh4[                                        data$item25 == 1] <- NA

data$rh5[ data$item122 > 3 & data$item207 > 3 &  data$item26 >  1] <- 1        
data$rh5[(data$item122 < 4 | data$item207 < 4) & data$item26 >  1] <- 0
data$rh5[                                        data$item26 == 1] <- NA

data$rh6[ data$item123 > 3 & data$item208 > 3 &  data$item27 >  1] <- 1        
data$rh6[(data$item123 < 4 | data$item208 < 4) & data$item27 >  1] <- 0
data$rh6[                                        data$item27 == 1] <- NA

data$rh7[ data$item124 > 3 & data$item209 > 3 &  data$item28 >  1] <- 1        
data$rh7[(data$item124 < 4 | data$item209 < 4) & data$item28 >  1] <- 0
data$rh7[                                        data$item28 == 1] <- NA

data$rh8[ data$item125 > 3 & data$item210 > 3 &  data$item29 >  1] <- 1        
data$rh8[(data$item125 < 4 | data$item210 < 4) & data$item29 >  1] <- 0
data$rh8[                                        data$item29 == 1] <- NA

data$rh9[ data$item126 > 3 & data$item211 > 3 &  data$item30 >  1] <- 1        
data$rh9[(data$item126 < 4 | data$item211 < 4) & data$item30 >  1] <- 0
data$rh9[                                        data$item30 == 1] <- NA

data$rh10[ data$item127 > 3 & data$item212 > 3 &  data$item31 >  1] <- 1        
data$rh10[(data$item127 < 4 | data$item212 < 4) & data$item31 >  1] <- 0
data$rh10[                                        data$item31 == 1] <- NA

data$rh11[ data$item128 > 3 & data$item213 > 3 &  data$item32 >  1] <- 1        
data$rh11[(data$item128 < 4 | data$item213 < 4) & data$item32 >  1] <- 0
data$rh11[                                        data$item32 == 1] <- NA

data$rh12[ data$item129 > 3 & data$item214 > 3 &  data$item42 >  1] <- 1        
data$rh12[(data$item129 < 4 | data$item214 < 4) & data$item42 >  1] <- 0
data$rh12[                                        data$item42 == 1] <- NA

data$rh13[ data$item130 > 3 & data$item215 > 3 &  data$item43 >  1] <- 1        
data$rh13[(data$item130 < 4 | data$item215 < 4) & data$item43 >  1] <- 0
data$rh13[                                        data$item43 == 1] <- NA

data$rh14[ data$item131 > 3 & data$item216 > 3 &  data$item44 >  1] <- 1        
data$rh14[(data$item131 < 4 | data$item216 < 4) & data$item44 >  1] <- 0
data$rh14[                                        data$item44 == 1] <- NA

data$rh15[ data$item132 > 3 & data$item217 > 3 &  data$item45 >  1] <- 1        
data$rh15[(data$item132 < 4 | data$item217 < 4) & data$item45 >  1] <- 0
data$rh15[                                        data$item45 == 1] <- NA

data$rh16[ data$item133 > 3 & data$item218 > 3 &  data$item46 >  1] <- 1        
data$rh16[(data$item133 < 4 | data$item218 < 4) & data$item46 >  1] <- 0
data$rh16[                                        data$item46 == 1] <- NA

data$rh17[ data$item134 > 3 & data$item219 > 3 &  data$item47 >  1] <- 1        
data$rh17[(data$item134 < 4 | data$item219 < 4) & data$item47 >  1] <- 0
data$rh17[                                        data$item47 == 1] <- NA

data$rh18[ data$item135 > 3 & data$item220 > 3 &  data$item48 >  1] <- 1        
data$rh18[(data$item135 < 4 | data$item220 < 4) & data$item48 >  1] <- 0
data$rh18[                                        data$item48 == 1] <- NA

data$rh19[ data$item136 > 3 & data$item221 > 3 &  data$item49 >  1] <- 1        
data$rh19[(data$item136 < 4 | data$item221 < 4) & data$item49 >  1] <- 0
data$rh19[                                        data$item49 == 1] <- NA

data$rh20[ data$item137 > 3 & data$item222 > 3 &  data$item50 >  1] <- 1        
data$rh20[(data$item137 < 4 | data$item222 < 4) & data$item50 >  1] <- 0
data$rh20[                                        data$item50 == 1] <- NA

data$rh21[ data$item138 > 3 & data$item223 > 3 &  data$item52 >  1] <- 1        
data$rh21[(data$item138 < 4 | data$item223 < 4) & data$item52 >  1] <- 0
data$rh21[                                        data$item52 == 1] <- NA

data$rh22[ data$item139 > 3 & data$item224 > 3 &  data$item53 >  1] <- 1        
data$rh22[(data$item139 < 4 | data$item224 < 4) & data$item53 >  1] <- 0
data$rh22[                                        data$item53 == 1] <- NA

data$rh23[ data$item140 > 3 & data$item225 > 3 &  data$item54 >  1] <- 1        
data$rh23[(data$item140 < 4 | data$item225 < 4) & data$item54 >  1] <- 0
data$rh23[                                        data$item54 == 1] <- NA

data$rh24[ data$item141 > 3 & data$item226 > 3 &  data$item55 >  1] <- 1        
data$rh24[(data$item141 < 4 | data$item226 < 4) & data$item55 >  1] <- 0
data$rh24[                                        data$item55 == 1] <- NA

data$rh25[ data$item142 > 3 & data$item227 > 3 &  data$item56 >  1] <- 1        
data$rh25[(data$item142 < 4 | data$item227 < 4) & data$item56 >  1] <- 0
data$rh25[                                        data$item56 == 1] <- NA

data$rh26[ data$item143 > 3 & data$item228 > 3 &  data$item57 >  1] <- 1        
data$rh26[(data$item143 < 4 | data$item228 < 4) & data$item57 >  1] <- 0
data$rh26[                                        data$item57 == 1] <- NA

data$rh27[ data$item144 > 3 & data$item229 > 3 &  data$item58 >  1] <- 1        
data$rh27[(data$item144 < 4 | data$item229 < 4) & data$item58 >  1] <- 0
data$rh27[                                        data$item58 == 1] <- NA

data$rh28[ data$item146 > 3 & data$item230 > 3 &  data$item59 >  1] <- 1        
data$rh28[(data$item146 < 4 | data$item230 < 4) & data$item59 >  1] <- 0
data$rh28[                                        data$item59 == 1] <- NA

data$rh29[ data$item147 > 3 & data$item231 > 3 &  data$item60 >  1] <- 1        
data$rh29[(data$item147 < 4 | data$item231 < 4) & data$item60 >  1] <- 0
data$rh29[                                        data$item60 == 1] <- NA

data$rh30[ data$item148 > 3 & data$item232 > 3 &  data$item62 >  1] <- 1        
data$rh30[(data$item148 < 4 | data$item232 < 4) & data$item62 >  1] <- 0
data$rh30[                                        data$item62 == 1] <- NA

data$rh31[ data$item149 > 3 & data$item233 > 3 &  data$item63 >  1] <- 1        
data$rh31[(data$item149 < 4 | data$item233 < 4) & data$item63 >  1] <- 0
data$rh31[                                        data$item63 == 1] <- NA

data$rh32[ data$item150 > 3 & data$item234 > 3 &  data$item64 >  1] <- 1        
data$rh32[(data$item150 < 4 | data$item234 < 4) & data$item64 >  1] <- 0
data$rh32[                                        data$item64 == 1] <- NA

data$rh33[ data$item151 > 3 & data$item235 > 3 &  data$item65 >  1] <- 1        
data$rh33[(data$item151 < 4 | data$item235 < 4) & data$item65 >  1] <- 0
data$rh33[                                        data$item65 == 1] <- NA

data$rh34[ data$item152 > 3 & data$item236 > 3 &  data$item67 >  1] <- 1        
data$rh34[(data$item152 < 4 | data$item236 < 4) & data$item67 >  1] <- 0
data$rh34[                                        data$item67 == 1] <- NA

data$rh35[ data$item153 > 3 & data$item237 > 3 &  data$item68 >  1] <- 1        
data$rh35[(data$item153 < 4 | data$item237 < 4) & data$item68 >  1] <- 0
data$rh35[                                        data$item68 == 1] <- NA

data$rh36[ data$item154 > 3 & data$item238 > 3 &  data$item69 >  1] <- 1        
data$rh36[(data$item154 < 4 | data$item238 < 4) & data$item69 >  1] <- 0
data$rh36[                                        data$item69 == 1] <- NA

data$rh37[ data$item155 > 3 & data$item239 > 3 &  data$item70 >  1] <- 1        
data$rh37[(data$item155 < 4 | data$item239 < 4) & data$item70 >  1] <- 0
data$rh37[                                        data$item70 == 1] <- NA

data$rh38[ data$item156 > 3 & data$item240 > 3 &  data$item71 >  1] <- 1        
data$rh38[(data$item156 < 4 | data$item240 < 4) & data$item71 >  1] <- 0
data$rh38[                                        data$item71 == 1] <- NA

data$rh39[ data$item157 > 3 & data$item241 > 3 &  data$item72 >  1] <- 1        
data$rh39[(data$item157 < 4 | data$item241 < 4) & data$item72 >  1] <- 0
data$rh39[                                        data$item72 == 1] <- NA

data$rh40[ data$item158 > 3 & data$item242 > 3 &  data$item73 >  1] <- 1        
data$rh40[(data$item158 < 4 | data$item242 < 4) & data$item73 >  1] <- 0
data$rh40[                                        data$item73 == 1] <- NA

data$rh41[ data$item159 > 3 & data$item243 > 3 &  data$item74 >  1] <- 1        
data$rh41[(data$item159 < 4 | data$item243 < 4) & data$item74 >  1] <- 0
data$rh41[                                        data$item74 == 1] <- NA

data$rh42[ data$item160 > 3 & data$item244 > 3 &  data$item75 >  1] <- 1        
data$rh42[(data$item160 < 4 | data$item244 < 4) & data$item75 >  1] <- 0
data$rh42[                                        data$item75 == 1] <- NA

data$rh43[ data$item161 > 3 & data$item245 > 3 &  data$item76 >  1] <- 1        
data$rh43[(data$item161 < 4 | data$item245 < 4) & data$item76 >  1] <- 0
data$rh43[                                        data$item76 == 1] <- NA

data$rh44[ data$item162 > 3 & data$item246 > 3 &  data$item77 >  1] <- 1        
data$rh44[(data$item162 < 4 | data$item246 < 4) & data$item77 >  1] <- 0
data$rh44[                                        data$item77 == 1] <- NA

data$rh45[ data$item163 > 3 & data$item247 > 3 &  data$item78 >  1] <- 1        
data$rh45[(data$item163 < 4 | data$item247 < 4) & data$item78 >  1] <- 0
data$rh45[                                        data$item78 == 1] <- NA

data$rh46[ data$item164 > 3 & data$item249 > 3 &  data$item79 >  1] <- 1        
data$rh46[(data$item164 < 4 | data$item249 < 4) & data$item79 >  1] <- 0
data$rh46[                                        data$item79 == 1] <- NA

data$rh47[ data$item165 > 3 & data$item250 > 3 &  data$item80 >  1] <- 1        
data$rh47[(data$item165 < 4 | data$item250 < 4) & data$item80 >  1] <- 0
data$rh47[                                        data$item80 == 1] <- NA

data$rh48[ data$item166 > 3 & data$item251 > 3 &  data$item81 >  1] <- 1        
data$rh48[(data$item166 < 4 | data$item251 < 4) & data$item81 >  1] <- 0
data$rh48[                                        data$item81 == 1] <- NA

data$rh49[ data$item167 > 3 & data$item252 > 3 &  data$item82 >  1] <- 1        
data$rh49[(data$item167 < 4 | data$item252 < 4) & data$item82 >  1] <- 0
data$rh49[                                        data$item82 == 1] <- NA

data$rh50[ data$item168 > 3 & data$item253 > 3 &  data$item83 >  1] <- 1        
data$rh50[(data$item168 < 4 | data$item253 < 4) & data$item83 >  1] <- 0
data$rh50[                                        data$item83 == 1] <- NA

data$rh51[ data$item169 > 3 & data$item254 > 3 &  data$item84 >  1] <- 1        
data$rh51[(data$item169 < 4 | data$item254 < 4) & data$item84 >  1] <- 0
data$rh51[                                        data$item84 == 1] <- NA

data$rh52[ data$item170 > 3 & data$item255 > 3 &  data$item85 >  1] <- 1        
data$rh52[(data$item170 < 4 | data$item255 < 4) & data$item85 >  1] <- 0
data$rh52[                                        data$item85 == 1] <- NA

data$rh53[ data$item171 > 3 & data$item256 > 3 &  data$item86 >  1] <- 1        
data$rh53[(data$item171 < 4 | data$item256 < 4) & data$item86 >  1] <- 0
data$rh53[                                        data$item86 == 1] <- NA

data$rh54[ data$item172 > 3 & data$item257 > 3 &  data$item87 >  1] <- 1        
data$rh54[(data$item172 < 4 | data$item257 < 4) & data$item87 >  1] <- 0
data$rh54[                                        data$item87 == 1] <- NA

data$rh55[ data$item173 > 3 & data$item258 > 3 &  data$item88 >  1] <- 1        
data$rh55[(data$item173 < 4 | data$item258 < 4) & data$item88 >  1] <- 0
data$rh55[                                        data$item88 == 1] <- NA

data$rh56[ data$item174 > 3 & data$item259 > 3 &  data$item89 >  1] <- 1        
data$rh56[(data$item174 < 4 | data$item259 < 4) & data$item89 >  1] <- 0
data$rh56[                                        data$item89 == 1] <- NA

data$rh57[ data$item175 > 3 & data$item260 > 3 &  data$item90 >  1] <- 1        
data$rh57[(data$item175 < 4 | data$item260 < 4) & data$item90 >  1] <- 0
data$rh57[                                        data$item90 == 1] <- NA

data$rh58[ data$item176 > 3 & data$item261 > 3 &  data$item91 >  1] <- 1        
data$rh58[(data$item176 < 4 | data$item261 < 4) & data$item91 >  1] <- 0
data$rh58[                                        data$item91 == 1] <- NA

data$rh59[ data$item177 > 3 & data$item262 > 3 &  data$item92 >  1] <- 1        
data$rh59[(data$item177 < 4 | data$item262 < 4) & data$item92 >  1] <- 0
data$rh59[                                        data$item92 == 1] <- NA

data$rh60[ data$item178 > 3 & data$item263 > 3 &  data$item93 >  1] <- 1        
data$rh60[(data$item178 < 4 | data$item263 < 4) & data$item93 >  1] <- 0
data$rh60[                                        data$item93 == 1] <- NA

data$rh61[ data$item179 > 3 & data$item264 > 3 &  data$item94 >  1] <- 1        
data$rh61[(data$item179 < 4 | data$item264 < 4) & data$item94 >  1] <- 0
data$rh61[                                        data$item94 == 1] <- NA

data$rh62[ data$item180 > 3 & data$item265 > 3 &  data$item95 >  1] <- 1        
data$rh62[(data$item180 < 4 | data$item265 < 4) & data$item95 >  1] <- 0
data$rh62[                                        data$item95 == 1] <- NA

data$rh63[ data$item181 > 3 & data$item266 > 3 &  data$item96 >  1] <- 1        
data$rh63[(data$item181 < 4 | data$item266 < 4) & data$item96 >  1] <- 0
data$rh63[                                        data$item96 == 1] <- NA

data$rh64[ data$item182 > 3 & data$item267 > 3 &  data$item97 >  1] <- 1        
data$rh64[(data$item182 < 4 | data$item267 < 4) & data$item97 >  1] <- 0
data$rh64[                                        data$item97 == 1] <- NA

data$rh65[ data$item183 > 3 & data$item268 > 3 &  data$item98 >  1] <- 1        
data$rh65[(data$item183 < 4 | data$item268 < 4) & data$item98 >  1] <- 0
data$rh65[                                        data$item98 == 1] <- NA

data$rh66[ data$item184 > 3 & data$item269 > 3 &  data$item99 >  1] <- 1        
data$rh66[(data$item184 < 4 | data$item269 < 4) & data$item99 >  1] <- 0
data$rh66[                                        data$item99 == 1] <- NA

data$rh67[ data$item185 > 3 & data$item270 > 3 &  data$item100 >  1] <- 1        
data$rh67[(data$item185 < 4 | data$item270 < 4) & data$item100 >  1] <- 0
data$rh67[                                        data$item100 == 1] <- NA

data$rh68[ data$item186 > 3 & data$item271 > 3 &  data$item101 >  1] <- 1        
data$rh68[(data$item186 < 4 | data$item271 < 4) & data$item101 >  1] <- 0
data$rh68[                                        data$item101 == 1] <- NA

data$rh69[ data$item187 > 3 & data$item272 > 3 &  data$item102 >  1] <- 1        
data$rh69[(data$item187 < 4 | data$item272 < 4) & data$item102 >  1] <- 0
data$rh69[                                        data$item102 == 1] <- NA

data$rh70[ data$item188 > 3 & data$item273 > 3 &  data$item103 >  1] <- 1        
data$rh70[(data$item188 < 4 | data$item273 < 4) & data$item103 >  1] <- 0
data$rh70[                                        data$item103 == 1] <- NA

data$rh71[ data$item189 > 3 & data$item274 > 3 &  data$item104 >  1] <- 1        
data$rh71[(data$item189 < 4 | data$item274 < 4) & data$item104 >  1] <- 0
data$rh71[                                        data$item104 == 1] <- NA

data$rh72[ data$item190 > 3 & data$item275 > 3 &  data$item105 >  1] <- 1        
data$rh72[(data$item190 < 4 | data$item275 < 4) & data$item105 >  1] <- 0
data$rh72[                                        data$item105 == 1] <- NA

data$rh73[ data$item191 > 3 & data$item276 > 3 &  data$item106 >  1] <- 1        
data$rh73[(data$item191 < 4 | data$item276 < 4) & data$item106 >  1] <- 0
data$rh73[                                        data$item106 == 1] <- NA

data$rh74[ data$item192 > 3 & data$item277 > 3 &  data$item107 >  1] <- 1        
data$rh74[(data$item192 < 4 | data$item277 < 4) & data$item107 >  1] <- 0
data$rh74[                                        data$item107 == 1] <- NA

data$rh75[ data$item193 > 3 & data$item278 > 3 &  data$item108 >  1] <- 1        
data$rh75[(data$item193 < 4 | data$item278 < 4) & data$item108 >  1] <- 0
data$rh75[                                        data$item108 == 1] <- NA

data$rh76[ data$item194 > 3 & data$item279 > 3 &  data$item109 >  1] <- 1        
data$rh76[(data$item194 < 4 | data$item279 < 4) & data$item109 >  1] <- 0
data$rh76[                                        data$item109 == 1] <- NA

data$rh77[ data$item195 > 3 & data$item280 > 3 &  data$item110 >  1] <- 1        
data$rh77[(data$item195 < 4 | data$item280 < 4) & data$item110 >  1] <- 0
data$rh77[                                        data$item110 == 1] <- NA

data$rh78[ data$item196 > 3 & data$item281 > 3 &  data$item111 >  1] <- 1        
data$rh78[(data$item196 < 4 | data$item281 < 4) & data$item111 >  1] <- 0
data$rh78[                                        data$item111 == 1] <- NA

data$rh79[ data$item197 > 3 & data$item282 > 3 &  data$item112 >  1] <- 1        
data$rh79[(data$item197 < 4 | data$item282 < 4) & data$item112 >  1] <- 0
data$rh79[                                        data$item112 == 1] <- NA

data$rh80[ data$item198 > 3 & data$item283 > 3 &  data$item113 >  1] <- 1        
data$rh80[(data$item198 < 4 | data$item283 < 4) & data$item113 >  1] <- 0
data$rh80[                                        data$item113 == 1] <- NA

data$rh81[ data$item199 > 3 & data$item284 > 3 &  data$item114 >  1] <- 1        
data$rh81[(data$item199 < 4 | data$item284 < 4) & data$item114 >  1] <- 0
data$rh81[                                        data$item114 == 1] <- NA

data$rh82[ data$item200 > 3 & data$item285 > 3 &  data$item115 >  1] <- 1        
data$rh82[(data$item200 < 4 | data$item285 < 4) & data$item115 >  1] <- 0
data$rh82[                                        data$item115 == 1] <- NA

data$rh83[ data$item201 > 3 & data$item286 > 3 &  data$item116 >  1] <- 1        
data$rh83[(data$item201 < 4 | data$item286 < 4) & data$item116 >  1] <- 0
data$rh83[                                        data$item116 == 1] <- NA

data$rh84[ data$item202 > 3 & data$item287 > 3 &  data$item117 >  1] <- 1        
data$rh84[(data$item202 < 4 | data$item287 < 4) & data$item117 >  1] <- 0
data$rh84[                                        data$item117 == 1] <- NA

@@

data$rc1[ data$item118 > 3 & data$item288 > 3 &  data$item22 >  1] <- 1        
data$rc1[(data$item118 < 4 | data$item288 < 4) & data$item22 >  1] <- 0
data$rc1[                                        data$item22 == 1] <- NA

data$rc2[ data$item119 > 3 & data$item289 > 3 &  data$item23 >  1] <- 1        
data$rc2[(data$item119 < 4 | data$item289 < 4) & data$item23 >  1] <- 0
data$rc2[                                        data$item23 == 1] <- NA

data$rc3[ data$item120 > 3 & data$item290 > 3 &  data$item24 >  1] <- 1        
data$rc3[(data$item120 < 4 | data$item290 < 4) & data$item24 >  1] <- 0
data$rc3[                                        data$item24 == 1] <- NA

data$rc4[ data$item121 > 3 & data$item291 > 3 &  data$item25 >  1] <- 1        
data$rc4[(data$item121 < 4 | data$item291 < 4) & data$item25 >  1] <- 0
data$rc4[                                        data$item25 == 1] <- NA

data$rc5[ data$item122 > 3 & data$item292 > 3 &  data$item26 >  1] <- 1        
data$rc5[(data$item122 < 4 | data$item292 < 4) & data$item26 >  1] <- 0
data$rc5[                                        data$item26 == 1] <- NA

data$rc6[ data$item123 > 3 & data$item293 > 3 &  data$item27 >  1] <- 1        
data$rc6[(data$item123 < 4 | data$item293 < 4) & data$item27 >  1] <- 0
data$rc6[                                        data$item27 == 1] <- NA

data$rc7[ data$item124 > 3 & data$item294 > 3 &  data$item28 >  1] <- 1        
data$rc7[(data$item124 < 4 | data$item294 < 4) & data$item28 >  1] <- 0
data$rc7[                                        data$item28 == 1] <- NA

data$rc8[ data$item125 > 3 & data$item295 > 3 &  data$item29 >  1] <- 1        
data$rc8[(data$item125 < 4 | data$item295 < 4) & data$item29 >  1] <- 0
data$rc8[                                        data$item29 == 1] <- NA

data$rc9[ data$item126 > 3 & data$item296 > 3 &  data$item30 >  1] <- 1        
data$rc9[(data$item126 < 4 | data$item296 < 4) & data$item30 >  1] <- 0
data$rc9[                                        data$item30 == 1] <- NA

data$rc10[ data$item127 > 3 & data$item297 > 3 &  data$item31 >  1] <- 1        
data$rc10[(data$item127 < 4 | data$item297 < 4) & data$item31 >  1] <- 0
data$rc10[                                        data$item31 == 1] <- NA

data$rc11[ data$item128 > 3 & data$item298 > 3 &  data$item32 >  1] <- 1        
data$rc11[(data$item128 < 4 | data$item298 < 4) & data$item32 >  1] <- 0
data$rc11[                                        data$item32 == 1] <- NA

data$rc12[ data$item129 > 3 & data$item299 > 3 &  data$item42 >  1] <- 1        
data$rc12[(data$item129 < 4 | data$item299 < 4) & data$item42 >  1] <- 0
data$rc12[                                        data$item42 == 1] <- NA

data$rc13[ data$item130 > 3 & data$item300 > 3 &  data$item43 >  1] <- 1        
data$rc13[(data$item130 < 4 | data$item300 < 4) & data$item43 >  1] <- 0
data$rc13[                                        data$item43 == 1] <- NA

data$rc14[ data$item131 > 3 & data$item301 > 3 &  data$item44 >  1] <- 1        
data$rc14[(data$item131 < 4 | data$item301 < 4) & data$item44 >  1] <- 0
data$rc14[                                        data$item44 == 1] <- NA

data$rc15[ data$item132 > 3 & data$item302 > 3 &  data$item45 >  1] <- 1        
data$rc15[(data$item132 < 4 | data$item302 < 4) & data$item45 >  1] <- 0
data$rc15[                                        data$item45 == 1] <- NA

data$rc16[ data$item133 > 3 & data$item303 > 3 &  data$item46 >  1] <- 1        
data$rc16[(data$item133 < 4 | data$item303 < 4) & data$item46 >  1] <- 0
data$rc16[                                        data$item46 == 1] <- NA

data$rc17[ data$item134 > 3 & data$item304 > 3 &  data$item47 >  1] <- 1        
data$rc17[(data$item134 < 4 | data$item304 < 4) & data$item47 >  1] <- 0
data$rc17[                                        data$item47 == 1] <- NA
